Micromechanism of Cold Deformation of Two Phase Polycrystalline Ti-Al Alloy with void

### 2018-11-23 draft/alexpub.tex
add

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{img/slice-view}
	\caption{Model of the simulation(a) and sliced view of the model with no void(b), with void inside $\alpha_2$ phase(c) with void at $\alpha_2 / \gamma$ interface(d)}
	\label{fig:model-creation}
\end{figure}

>>>>

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{img/slice-view}
	\caption{Model of the simulation(a) and sliced view of the model with no void(b), inside $\alpha_2$ phase(c) at $\alpha_2 / \gamma$ phase boundary(d)}
	\label{fig:model-creation}
\end{figure}
